\bf Hierarchical Network Structure Promotes Dynamical Robustness

### 2015-01-15 tex/abstract.tex
minor changes to abstract

\begin{abstract}
Here we analyze the stability and robustness of a large class of dynamical systems. In particular, we precisely determine the probability distribution of robustness over system connectivity, which has significant implications from the study of metabolic to gene-regulatory to ecosystem network dynamics, for systems with two and three interacting components. We show that robustness is classified by the number of links between strongly connected components of the graph representing the underlying system connectivity leading to the conclusion that the most robust systems are also the most hierarchical. We also demonstrate that permutation of strongly connected components is a fundamental symmetry of dynamical robustness. This results in the classification of the dynamical robustness of biological networks based upon a purely topological property.
\end{abstract}

>>>>

\begin{abstract}
Here we analyze the stability and robustness of a large class of dynamical systems. We determine the probability distribution of robustness over system connectivity, which has significant implications from the study of metabolic to gene-regulatory to ecosystem network dynamics. We show that robustness is classified by the number of links between strongly connected components of the graph representing the underlying system connectivity leading to the conclusion that the most robust systems are also the most hierarchical. We also demonstrate that permutation of strongly connected components is a fundamental symmetry of dynamical robustness. This results in the classification of the dynamical robustness of biological networks based upon a purely topological property.
\end{abstract}
